Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-12-17 MDPI_submission.Rmd
Commit 2023-12-16 15:10
Commit 2023-12-17 20:14

In the final [dataset $23.3\%$ of the 1-minute data were
identified as under clear-sky conditions and]{.mark} $43\%$ [as]{.mark}
under cloud-sky conditions.

@@

The solar zenith angle is a major factor affecting the SDR, since
increases in SZA leads to enhancement of the radiation path in the
atmosphere, especially in urban environments with human activities
emitting aerosols 
[@Wang2021].
In order to estimate the effect of SZA on the SDR trends, we grouped the anomaly data in bins of $1^\circ$ SZA, and calculated the overall trend for each bin before noon and after noon (Figure\ \ref{fig:szatrends}).
Although there are seasonal dependencies of the minimum SZA (see Appendix, Figure\ \ref{fig:SZAtrendSeason}), these dependencies would not be further examined here.
For all-sky and clear-sky conditions the brightening effect of SDR (positive trend) is stronger for large SZAs (Figures\ \ref{fig:szatrends-1} and \ref{fig:szatrends-2}).
The trends in the morning and afternoon hours are more or less consistent with small differences, which can be attributed to systematic diurnal variations of aerosols, particularly during the warm period of the year [@Wang2021].
For cloudy-sky conditions (Figure\ \ref{fig:szatrends-3}), we can not discern any significant dependence of the SDR trend with SZA.
For SZAs $16^\circ$ - $50^\circ$, the trends range within about $\pm 0.2\,\%/y$, with a weak statistical significance.
Between $50^\circ$ and $75^\circ$ SZA the trends for the period before noon are stronger and negative, possibly associated with stronger attenuation by clouds under oblique incidence angles.

>>>>

@@

The solar zenith angle is a major factor affecting the SDR, since
increases in SZA leads to enhancement of the radiation path in the
atmosphere, especially in urban environments with human activities
emitting aerosols 
[@Wang2021].
In order to estimate the effect of SZA on the SDR trends, we grouped the data in bins of $1^\circ$ SZA, and calculated the overall trend for each bin, separately for the daily
periods before noon and after noon (Figure\ \ref{fig:szatrends}).
Although there are seasonal dependencies of the minimum SZA (see Appendix, Figure\ \ref{fig:SZAtrendSeason}), these dependencies are not discussed further.

For all-sky conditions the brightening effect of SDR (positive trend) is
stronger for large SZAs (Figures\ \ref{fig:szatrends-1} and \ref{fig:szatrends-2}).
The trends in the morning and afternoon hours are more or less consistent with small differences, which can be attributed to systematic diurnal variations of aerosols, particularly during the warm period of the year [@Wang2021].

For cloudy-sky conditions (Figure\ \ref{fig:szatrends-3}), we can not discern any significant dependence of the SDR trend with SZA.
For SZAs $16^\circ$ - $50^\circ$, the trends range within about $\pm 0.2\,\%/y$, with a weak statistical significance.
Between $50^\circ$ and $75^\circ$ SZA the trends for the period before noon are stronger and negative, possibly associated with stronger attenuation by clouds under oblique incidence angles.

### 2023-12-17 MDPI_submission.tex
Commit 2023-12-16 15:10
Commit 2023-12-17 20:14

In the final \hl{dataset \(23.3\%\) of the 1-minute data were identified
as under clear-sky conditions and} \(43\%\) \hl{as} under cloud-sky
conditions.

@@

The solar zenith angle is a major factor affecting the SDR, since
increases in SZA leads to enhancement of the radiation path in the
atmosphere, especially in urban environments with human activities
emitting aerosols \citep{Wang2021}. In order to estimate the effect of
SZA on the SDR trends, we grouped the anomaly data in bins of
\(1^\circ\) SZA, and calculated the overall trend for each bin before
noon and after noon (Figure~\ref{fig:szatrends}). Although there are
seasonal dependencies of the minimum SZA (see Appendix,
Figure~\ref{fig:SZAtrendSeason}), these dependencies would not be
further examined here. For all-sky and clear-sky conditions the
brightening effect of SDR (positive trend) is stronger for large SZAs
(Figures~\ref{fig:szatrends-1} and \ref{fig:szatrends-2}). The trends in
the morning and afternoon hours are more or less consistent with small
differences, which can be attributed to systematic diurnal variations of
aerosols, particularly during the warm period of the year
\citep{Wang2021}. For cloudy-sky conditions
(Figure~\ref{fig:szatrends-3}), we can not discern any significant
dependence of the SDR trend with SZA. For SZAs \(16^\circ\) -
\(50^\circ\), the trends range within about \(\pm 0.2\,\%/y\), with a
weak statistical significance. Between \(50^\circ\) and \(75^\circ\) SZA
the trends for the period before noon are stronger and negative,
possibly associated with stronger attenuation by clouds under oblique
incidence angles.

>>>>

@@

The solar zenith angle is a major factor affecting the SDR, since
increases in SZA leads to enhancement of the radiation path in the
atmosphere, especially in urban environments with human activities
emitting aerosols \citep{Wang2021}. In order to estimate the effect of
SZA on the SDR trends, we grouped the data in bins of \(1^\circ\) SZA,
and calculated the overall trend for each bin, separately for the daily
periods before noon and after noon (Figure~\ref{fig:szatrends}).
Although there are seasonal dependencies of the minimum SZA (see
Appendix, Figure~\ref{fig:SZAtrendSeason}), these dependencies are not
discussed further.

For all-sky conditions the brightening effect of SDR (positive trend) is
stronger for large SZAs (Figures~\ref{fig:szatrends-1} and
\ref{fig:szatrends-2}). The trends in the morning and afternoon hours
are more or less consistent with small differences, which can be
attributed to systematic diurnal variations of aerosols, particularly
during the warm period of the year \citep{Wang2021}.

For cloudy-sky conditions (Figure~\ref{fig:szatrends-3}), we can not
discern any significant dependence of the SDR trend with SZA. For SZAs
\(16^\circ\) - \(50^\circ\), the trends range within about
\(\pm 0.2\,\%/y\), with a weak statistical significance. Between
\(50^\circ\) and \(75^\circ\) SZA the trends for the period before noon
are stronger and negative, possibly associated with stronger attenuation
by clouds under oblique incidence angles.
